### 2014-04-28 docs/seminar/introduction.tex
Merge branch 'CLEF2014' of https://github.com/neds/expert-retrieval-translators into CLEF2014
Conflicts:
	.gitignore

This paper addresses the problem of searching translators as experts. We offer a novel translator-expert retrieval platform and evaluate different expert retrieval methods based on the practical implementation of the platform. In contrast to common expert retrieval systems, we include significant factors of searching a translator (such as price and delivery time) in the automated decision process as well as the relevance of the documents each translator has previously translated to the query document. The proposed method has two distinct components: A proficiency estimation phase, in which different aggregation algorithms related to documents of translators have been studied and compared; and a Learning-to-Rank phase in which different features are tested under all state of the art Learning-to-Rank methods based on a manually created ground truth, which we make available together with the source code of our application under GPL\footnote{\url{https://github.com/neds/expert-retrieval-translators}}.

>>>>

This paper addresses the problem of searching translators as experts. We offer a novel translator-expert retrieval platform and evaluate different expert retrieval methods based on the practical implementation of the platform. In contrast to common expert retrieval systems, we include practical factors of searching a translator (such as price and delivery time) in the automated decision process as well as the relevance of the documents each translator has previously translated to the query document. The proposed method has two distinct components: A proficiency estimation phase, in which different aggregation algorithms related to documents of translators have been studied and compared; and a Learning-to-Rank phase in which different features are tested under all state of the art Learning-to-Rank methods based on a manually created ground truth, which we make available together with the source code of our application under GPL\footnote{\url{https://github.com/neds/expert-retrieval-translators}}. The contributions of the report are four-fold:
\begin{enumerate}
\item the application and adaptation of state-of-the-art IR methods to a new use-case
\item extensive evaluation in a realistic scenario, including non-topical relevance criteria as part of the evaluation
\item creation of a publicly available test collection
\end{enumerate}
